---
title: "Assignment 4"
output: html_notebook
---
Question 3:
Load the training (2014) and test (2015) data sets
```{r}
load("../data/eye_FR_testdata-1")
load("../data/eye_FR_traindata-1")
```
Load tidyverse, Magrittr, Psych, and vcd
```{r}
library(tidyverse)
library(magrittr)
install.packages("psych")
library(psych)
install.packages("vcd")
library(vcd)
```
Step 1: Describe eyewitness accuracy (lineupacc) in training data set
```{r}
traindata %>%  
    describe     
table(traindata$lineupacc)
```
From the second table above - note that of 117 participants, 55 people were incorrect in their response (false positives + false negatives), and 66 people were correct in their response (correct identification in a target present lineup, and correct rejection in a target absent lineup)
From the first table above:
"Particip" can be ignored - this is just the participant number
"Lineuptpta" refers to whether the lineup featured a target that was present in the simulated crime (TP = target present), or did not feature a target that was present in the simulated crime (TA = target absent). A value of 1 represents a target absent lineup, and a value of 2 represents a target present lineup. As the mean value is 1.5 - There were an (almost) equal number of target present and target absent conditions
"Lineupacc" refers to whether the participant gave a correct response (defined above; assigned a value of 1), or an incorrect response (defined above; assigned a value of 0). With a mean of 0.53, just over half of the participants were correct in their response
"Exposure" refers to the length of time the participant was exposed to the video of the simulated crime. Short exposure is a video of about 3 seconds (assigned a value of 2), and long exposure is a video of about 90 seconds (assigned a value of 1). The mean value is 1.5, indicating that (about) half of the participants had long exposure, while the other half had short exposure
"Confidence" refers to a self-rated scale of how confident the participant was that they had made the correct decision (defined above) on a scale ranging from 0 - 100. For this measure, there is missing data for 3 cases. Skewness and kurtosis statistics are in the acceptable range, suggesting a normal disttribution of data across this continuous variable. Participant responses spanned the full range of the scale (0-100), the mean is 55.77 (just over the half way mark), and the standard deviation is 31.59.
"Lineuprt" refers to lineup response time - the time (in milliseconds) that participants took before making a decision on whether the target was present or absent in the lineup. Response times ranged from 5009ms to 124143ms, which is a large range.The mean response time was 28423.79ms - well below the midpoint of the range.  The standard deviation is 22795.90ms - which means that 95% of the response times were below 74015.59ms (well below the max value of the range), and 99.7% of the response times were below 96811.49ms.
In light of the maximum value being 124143ms - this is suggestive that there may be outliers on the high end of the range.
Skewness and kurtosis statistics further suggest a non-normal distribution. This distribution will first be examined graphically - if it proves to be a non-normal distribution, a log10 transformation will be performed. If this does not correct the problem, outliers with values further than 3 standard deviations from the mean may need to be removed. 
"Automatic" refers to a self report measure - participants were asked to indicate whether they made their decision automatically or after much deliberation, on a scale from 1 to 5. It is unclear what these values represent.
"Facecomparison" refers to a self report measure - participants were asked if they rejected the lineup because the people in the lineup did not look like the target, on a scale from 1 to 5. It is unclear what these values represent.
____________________________________________________________________________
Step 1: Graphically investigate the distribution of continuous variables in training data
Graph 1: Confidence (confidence)
Graph 2: Response time (lineuprt)
```{r}
ggplot(data = traindata, mapping = aes(x = confidence))+
  geom_histogram(binwidth = 8)
  
ggplot(data = traindata, mapping = aes(x = lineuprt))+
  geom_histogram()

  
```
Step 2: Transform response time (lineuprt) to correct for the skew
```{r}
lineuprt_log <- (log10(traindata$lineuprt))
```
Step 3: Investigate distribution for log10 transformation of response time (lineuprt_log)
```{r}
describe(lineuprt_log) 
ggplot(data = traindata, mapping = aes(x = lineuprt_log))+
  geom_histogram()
```
Table 1 indicates that the unacceptable levels of skewness and kurtosis have been resolved with a log10 transformation. Graph 1 confirms this, although it appears there are still some outliers.
____________________________________________________________________________
Step 4: Test whether 1)confidence of response (confidence) is predictive of lineup accuracy (lineupacc), and 2)the transformed lineup response time (lineuprt_log) is predictive of eyewitness accuracy(lineupacc)
```{r}
ggplot(traindata, aes(x = confidence, y = lineupacc))+
  geom_point()+
    geom_jitter(height = .1, alpha = 0.3)+
    geom_smooth(method = "glm",
                se = F)

ggplot(traindata, aes(x = lineuprt_log, y = lineupacc))+
  geom_point()+
    geom_jitter(height = .1, alpha = 0.3)+
    geom_smooth(method = "glm",
                se = F)

```
Graph 1 suggestss that the more confident a participant is in their response, the more likely it is that they have given a correct reponse.
Graph 2 sugests that the longer it takes a participant to give a response, the less likely it is that they have given a correct response.






```{r}

```

```{r}

```

```{r}

```



```{r}

```

