---
title: "Assignment 4"
output: html_notebook
---
Question 3:
Load the training (2014) and test (2015) data sets
```{r}
load("../data/eye_FR_testdata-1")
load("../data/eye_FR_traindata-1")
```
Load tidyverse, Magrittr, Psych, caret, and vcd
```{r}
library(tidyverse)
library(magrittr)
install.packages("psych")
library(psych)
install.packages("vcd")
library(vcd)
install.packages("caret")
library(caret)
```
Question 3:
 1: Describe eyewitness accuracy (lineupacc) in training data set, as well as the properties of the other variables.
```{r}
traindata %>%  
    describe     
table(traindata$lineupacc)
```
From the second table above - note that of 117 participants, 55 people were incorrect in their response (false positives + false negatives), and 66 people were correct in their response (correct identification in a target present lineup, and correct rejection in a target absent lineup)
From the first table above:
"Particip" can be ignored - this is just the participant number
"Lineuptpta" refers to whether the lineup featured a target that was present in the simulated crime (TP = target present), or did not feature a target that was present in the simulated crime (TA = target absent). A value of 1 represents a target absent lineup, and a value of 2 represents a target present lineup. As the mean value is 1.5 - There were an (almost) equal number of target present and target absent conditions
"Lineupacc" refers to whether the participant gave a correct response (defined above; assigned a value of 1), or an incorrect response (defined above; assigned a value of 0). With a mean of 0.53, just over half of the participants were correct in their response
"Exposure" refers to the length of time the participant was exposed to the video of the simulated crime. Short exposure is a video of about 3 seconds (assigned a value of 2), and long exposure is a video of about 90 seconds (assigned a value of 1). The mean value is 1.5, indicating that (about) half of the participants had long exposure, while the other half had short exposure
"Confidence" refers to a self-rated scale of how confident the participant was that they had made the correct decision (defined above) on a scale ranging from 0 - 100. For this measure, there is missing data for 3 cases. Skewness and kurtosis statistics are in the acceptable range, suggesting a normal disttribution of data across this continuous variable. Participant responses spanned the full range of the scale (0-100), the mean is 55.77 (just over the half way mark), and the standard deviation is 31.59.
"Lineuprt" refers to lineup response time - the time (in milliseconds) that participants took before making a decision on whether the target was present or absent in the lineup. Response times ranged from 5009ms to 124143ms, which is a large range.The mean response time was 28423.79ms - well below the midpoint of the range.  The standard deviation is 22795.90ms - which means that 95% of the response times were below 74015.59ms (well below the max value of the range), and 99.7% of the response times were below 96811.49ms.
In light of the maximum value being 124143ms - this is suggestive that there may be outliers on the high end of the range.
Skewness and kurtosis statistics further suggest a non-normal distribution. This distribution will first be examined graphically - if it proves to be a non-normal distribution, a log10 transformation will be performed. If this does not correct the problem, outliers with values further than 3 standard deviations from the mean may need to be removed. 
"Automatic" refers to a self report measure - participants were asked to indicate whether they made their decision automatically or after much deliberation, on a scale from 1 to 5. It is unclear what these values represent.
"Facecomparison" refers to a self report measure - participants were asked if they rejected the lineup because the people in the lineup did not look like the target, on a scale from 1 to 5. It is unclear what these values represent.
____________________________________________________________________________
Step 1: Graphically investigate the distribution of continuous variables in training data
Graph 1: Confidence (confidence)
Graph 2: Response time (lineuprt)
```{r}
ggplot(data = traindata, mapping = aes(x = confidence))+
  geom_histogram(binwidth = 8)
  
ggplot(data = traindata, mapping = aes(x = lineuprt))+
  geom_histogram()

  
```
Step 2: Transform response time (lineuprt) to correct for the skew
```{r}
lineuprt_log <- (log10(traindata$lineuprt))
```
Step 3: Investigate distribution for log10 transformation of response time (lineuprt_log)
```{r}
describe(lineuprt_log) 
ggplot(data = traindata, mapping = aes(x = lineuprt_log))+
  geom_histogram()
```
Table 1 indicates that the unacceptable levels of skewness and kurtosis have been resolved with a log10 transformation. Graph 1 confirms this, although it appears there are still some outliers.
____________________________________________________________________________
Step 4: Test whether 1)confidence of response (confidence) is predictive of lineup accuracy (lineupacc), and 2)the transformed lineup response time (lineuprt_log) is predictive of eyewitness accuracy(lineupacc). These relationships will then each be faceted by target presence (lineuptpta), and length of initail exposure to target (exposure), to investigate whether these factors influence the abovementioned relationships.
```{r}
ggplot(traindata, aes(x = confidence, y = lineupacc))+
  geom_point()+
    geom_jitter(height = .1, alpha = 0.3)+
    geom_smooth(method = "glm",
                se = F)

ggplot(traindata, aes(x = lineuprt_log, y = lineupacc))+
  geom_point()+
    geom_jitter(height = .1, alpha = 0.3)+
    geom_smooth(method = "glm",
                se = F)
ggplot(traindata, aes(x = confidence, y = lineupacc))+
  geom_point()+
    geom_jitter(height = .1, alpha = 0.3)+
    geom_smooth(method = "glm",
                se = F)+
  facet_wrap(~lineuptpta)

ggplot(traindata, aes(x = lineuprt_log, y = lineupacc))+
  geom_point()+
    geom_jitter(height = .1, alpha = 0.3)+
    geom_smooth(method = "glm",
                se = F)+
facet_wrap(~lineuptpta)

ggplot(traindata, aes(x = confidence, y = lineupacc))+
  geom_point()+
    geom_jitter(height = .1, alpha = 0.3)+
    geom_smooth(method = "glm",
                se = F)+
  facet_wrap(~exposure)

ggplot(traindata, aes(x = lineuprt_log, y = lineupacc))+
  geom_point()+
    geom_jitter(height = .1, alpha = 0.3)+
    geom_smooth(method = "glm",
                se = F)+
  facet_wrap(~exposure)

```
Graph 1 suggests that the more confident a participant is in their response overall, the more likely it is that they have given a correct reponse.
Graph 2 sugests that the longer it takes a participant to give a response overall, the less likely it is that they have given a correct response.

Graph 3 suggests that the effect of confidence on accuracy is much stronger in target absence lineups than in target present lineups
Graph 4 suggests that the length of response time affects lineup accuracy negatively only in target absent lineups. This effect is almost null in target present lineups. 

Graph 5 suggests that the effect of confidence on accuracy is slightly stronger in the long video condition than in the short video condition (which is very weak)
Graph 6 suggests that length of response time negatively affects lineup accuracy for both the long and short video conditions

To summarise:
The more confident a participant is in their response, the more likely they are to be correct, specifically in a) target absent lineups, and b) when they had a longer initial exposure to the target (in the simulated crime video)
The longer it takes a participant to give their response to the lineup, the less likely they are to be correct, however only in target absent lineups, regardless of the initial length of exposure to the target
________________________________________________________________________
Question 4:
Step 1: Check whether lineup accuracy is predicted by confidence and response time (respectively)
```{r}
accuracy_model1 <- glm(lineupacc ~ confidence,
      family = "binomial", data = traindata)
summary(accuracy_model1)

accuracy_model2 <- glm(lineupacc ~ lineuprt_log,
      family = "binomial", data = traindata)
summary(accuracy_model2)
```
The above logistic regressions indicate that overall: confidence is significantly predictive of response accuracy, but response time is not
________________________________________________________________________
Step 2: Check whether these findings hold true over and above what is already accounted for by the 2 conditions (target present/absent and exposure)
```{r}
accuracy_model3 <- glm(lineupacc ~ lineuptpta + exposure + confidence,
      family = "binomial", data = traindata)
summary(accuracy_model3)
accuracy_model4 <- glm(lineupacc ~ lineuptpta + exposure + lineuprt_log,
      family = "binomial", data = traindata)
summary(accuracy_model4)
```
Both the presence/absence of the target and the length of initial exposure to the target are significantly predictive of lineup accuracy. Neither confidence nor response time significantly adds to this model
__________________________________________________________________________
Step 3: Check whether automatic recognition or face comparison add to the model over and above the conditions of the design
```{r}
accuracy_model5 <- glm(lineupacc ~ lineuptpta + exposure + automatic,
      family = "binomial", data = traindata)
summary(accuracy_model5)
accuracy_model6 <- glm(lineupacc ~ lineuptpta + exposure + facecomparison,
      family = "binomial", data = traindata)
summary(accuracy_model6)
```
Neither one of these variables adds to the model over and above the conditions of the experiment.
_______________________________________________________________________
Step 4: Check whether the predictive model holds true for the test data
```{r}
accuracy_model7 <- glm(lineupacc ~ lineuptpta + exposure,
      family = "binomial", data = testdata)
summary(accuracy_model7)
```
The model above confirms our findings in the training data set. Both the absence/presence of a target and the length of initial exposure to the target are significantly predictive of lineup accuracy. If the target is present, the participant is significantly more likely to respond inaccurately than if the target is absent. Furthermore, if the initial exposure is short, the participant is significantly more likely to respond inaccurately than if the initial exposure is long.
In conclusion: 1)Eye witnesses are more sucessful at correctly rejecting a lineup that doesnt contain the perpetrator, than they are at correctly identifying a perpetrator in a lineup where they are present. 2) Eye witnesses are more accurate when they have had a longer initial exposure (90s) to the perpetrator (i.e. during the crime), than they are if the initial exposure is very short (3s)
___________________________________________________________________________-
Question 5:
i) What is the probability that someone who is > 80% confident is accurate?
```{r}
accuracy_model8 <- glm(lineupacc ~ confidence,
      family = "binomial", data = traindata)
summary(accuracy_model8)
predict(accuracy_model8, 
        data.frame(confidence = 80), type = "response")
```
There is a 63% chance that someone who is > 80% confident is accurate

ii) What are the odds that someone who is >80% confident is accurate?
```{r}
x <- predict(accuracy_model8, 
        data.frame(confidence = 80), type = "response")
odds <- x/(1-x)
print(odds)
```
The odds of them being correct is 1.73

iii) What is the partial odds ratio in the relation between lineuptpta and accuracy of decision
```{r}
accuracy_model9 <- glm(lineupacc ~ lineuptpta + confidence,
      family = "binomial", data = traindata)
summary(accuracy_model9)
```
To convert partial logit to partial odds:
e^(-1.048236) = 0.35055558407 (partial odds)

b) Assess accuracy of model with confusion matrix
```{r}

```

```{r}
chdmodel1 <- glm(chd ~ tobacco, 
                 family = "binomial", data = saheart)
summary(chdmodel1)
predict(chdmodel1, 
        data.frame(tobacco = 30)) # logit
predict(chdmodel1, 
        data.frame(tobacco = 30), type = "response") # probability
x <- predict(chdmodel1, 
        data.frame(tobacco = 30), type="response")
odds <- x/(1-x)  # to get the answer in odds
print(odds)

predict(chdmodel1, 
        data.frame(tobacco = 19)) # logit
predict(chdmodel1, 
        data.frame(tobacco = 19), type = "response") # probability
x <- predict(chdmodel1, 
             data.frame(tobacco = 19), type="response")
odds <- x/(1-x)  # to get the answer in odds
print(odds)
```

```{r}

```

```{r}

```



```{r}

```

