---
title: "Assignment 4"
output: html_notebook
---
Question 3:
Load the training (2014) and test (2015) data sets
```{r}
load("../data/eye_FR_testdata-1")
load("../data/eye_FR_traindata-1")
```
Load tidyverse and Magrittr
```{r}
library(tidyverse)
library(magrittr)
```
Step 1: Investigate the distribution of continuous variables in training data
Graph 1: Confidence (confidence)
Graph 2: Response time (lineuprt)
```{r}
ggplot(data = traindata, mapping = aes(x = confidence))+
  geom_histogram(binwidth = 8)
  
ggplot(data = traindata, mapping = aes(x = lineuprt))+
  geom_histogram()

  
```
Step 2:
Test whether lineup response time (lineuprt) is predictive of eyewitness accuracy(lineupacc), faceted by whether the target is present (TP) or absent (TA)(linuptpta)
```{r}
ggplot(data = traindata, mapping = aes(x = lineuprt, y = lineupacc))+
  geom_jitter(alpha = 0.2)+
  geom_smooth()+
  facet_wrap(~lineuptpta)
```
Step 3: transform response time (lineuprt) to correct for the skew
```{r}
lineuprt_log <- (log10(traindata$lineuprt))
```
Step 4: Investigate distribution for log10 transformation of response time (lineuprt_log)
```{r}
ggplot(data = traindata, mapping = aes(x = lineuprt_log))+
  geom_histogram()
```
Step 5: Retest whether the transformed lineup response time (lineuprt_log) is predictive of eyewitness accuracy(lineupacc), faceted by whether the target is present (TP) or absent (TA)(linuptpta)
```{r}
ggplot(data = traindata, mapping = aes(x = lineuprt_log, y = lineupacc))+
  geom_jitter(alpha = 0.2)+
  geom_smooth()+
  facet_wrap(~lineuptpta)
```
Step 6: Test whether confidence of response (confidence) is predictive of lineup accuracy (lineupacc), faceted by whether the target is present (TP), or absent (TA)(lineuptpta)
```{r}
ggplot(data = traindata, mapping = aes(x = confidence, y = lineupacc))+
  geom_jitter(alpha = 0.2)+
  geom_smooth()+
  facet_wrap(~lineuptpta)
```

